25 years of Social Work Research

### 2015-02-22 dataCleaning.Rmd
Cleanup of document.

Everything written after this point was for the ebsco full data file (psycinof, swa, ssa).  The R objects have been all re-written and renamed.  The first thing to do is to append the ebscoFULL and proQuest objects.  Here is my recommended steps:

1.  Create a variable that takes the maximum values of the articleID from ebscoFULL
2.  Add the max value to the article ID of proQuest
3.  Write a function that matches the titles of ebscoFull with proQuest, grabs the ID, and then, eliminates the duplicates.  We have all the matching code in the original functions that you can grab.  
4.  Consider drawing on the pmatch.R function in the BWR folder.  This function forces all to lower, strips all the white space, and takes a subset of the characters (e.g., ~25 I think).  The advantage of this is to avoid the incorrect matching when colons are used.  Same title, but you get the idea of where things can go awry with title matching.  Test it extensively -- e.g., alphebatizing is also helpful.

Social work research can be really:  Bad
Social work research can be really: Bad
Social Work research can be really: bad
Social work research can be really: Bad
Social work research can be really: bad
Social Work research can be really:  bad

5.  Do necessary search and replace of subsequent code to get it working with the fully appended data file.

#Combines EbscoHost and ProQUest wrangles and eliminates duplicate article titles

library(dplyr)

@@

  #Strips out white space and punctuation to ensure small differences
  #in data entry are detected during duplicate elimination
  jointTitles$record<-gsub(" ","", jointTitles$record)

  #punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'
  #JointTitles$record<-gsub(punct, "", JointTitles$record)  
  jointTitles$record<-gsub("[[:punct:]]", "", jointTitles$record)

@@

  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
  #from duplicate entries
  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
  combined.DF<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

@@

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
```

# Pre-processing summary
```{r echo=FALSE}
full.df$record <- ifelse(full.df$record == 
        "Social Work & Social Sciences Review",     # Spelling difference
        "Social Work and Social Sciences Review", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
    "The British Journal Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)
```

Provided below is a summary of the datafile processed by `ebscoBWR` function before any cleaning procedures specifically for this project were employed, with the exception of resolving spelling errors or differences.  For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)

@@

# Data cleaning

## Year specification

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor")

@@

Exclusions were then made any of the three criteria

+ Journals that did not have clear evidence of a peer review process.  This was based on a review of the journals mission, scope, and whether an editorial board or group could be identified.

+ Journal titles that did not have any clear publication history based on a broad-based Internet search and other databases (e.g., ProQuest).  These exclusions are assumed to be data entry problems at time of indexing.

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Social Work Process",
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Proceedings of the National Conference of Social Work","Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", 
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", 
    "Social Work Yearbook",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" 
    )

@@

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
    "The British Journal of Pyschiatric Social Work", # Old
        "British Journal of Social Work",           # New title
                        full.df$record)

@@

## Intersection, Differences and Union

This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, _differences_, and _union_ of the lists.
```{r}
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

@@

hodge.swHistory.union <- union(hodge, unique.swHistory$record)
```

@@

@@

```{r}
sink(file = "JournalsMissed.txt")
print(sort(hodge.swHistory.diff))
sink()
```
This list shows the articles on the current study but not on Hodge.

@@

This list shows the union of lists -- that is, a full list of all titles by combining a list.  It would be useful to break out the former titles of journals, as well as the years of existence.  This would establish a complete listing of all social work journals, both current and historical.

```{r}
print(sort(hodge.swHistory.union))
```

>>>>

# Combines EbscoHost and ProQUest

This section ... wrangles and eliminates duplicate article titles

```{r appendData, comment=NA}

@@

#Strips out white space and punctuation to ensure small differences in data 
#entry are detected during duplicate elimination
jointTitles$record<-gsub(" ","", jointTitles$record)

jointTitles$record<-gsub("[[:punct:]]", "", jointTitles$record)

@@

#Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
#from duplicate entries
combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

rm(list=setdiff(ls(), "full.df"))

@@

# Data cleaning and pre-processing

## Narrow results to past 25 years

## Initial descriptive summary

@@

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "Professional Development in Education",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor")

@@

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Issues in Social Work Education", 
    "Maatskaplike Werk/Social Work",
    "Pediatric Social Work", 
    "Critical Social Work"
    )

@@

## Fix journal titles

Additional pre-processing was conducted on journal titles to resolve spelling errors or other minor title differences in the database. For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)  We also applied a global substitution of _and_ with _&_, as this was a common source for differences.

```{r echo=FALSE}
full.df$record <- ifelse(full.df$record == 
        "Social Work & Social Sciences Review",     # Spelling difference
        "Social Work and Social Sciences Review", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
    "The British Journal Social Work",          # Spelling difference
        "British Journal of Social Work",           
                        full.df$record)

#shortens Professional Development
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub(":.+", "", full.df$record), 
        full.df$record)

#shortens Canadian Social Work review by eliminating foreign title and is
#automatically combined with other short spelling
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub("(/R){1}.+", "", full.df$record), 
        full.df$record)

# shortens Contemporary Rural Social Work
full.df$record <- ifelse(full.df$attributes == "journal",
        gsub("\\s\\(.+", "", full.df$record), 
        full.df$record)

full.df$record <- ifelse(full.df$attributes == "journal", 
      gsub("and", "&", full.df$record), full.df$record)

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
    "The British Journal of Pyschiatric Social Work" | 
        full.df$record == 
    "The British Journal of Social Work", # Old
        "British Journal of Social Work",           # New title
                        full.df$record)

@@

# Comparison with Hodge

This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, and _differences_.

## Intersection

```{r}
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

@@

#hodge.swHistory.union <- union(hodge, unique.swHistory$record)
```

@@

## Differences

@@

```{r}
print(sort(hodge.swHistory.diff))
```
This list shows the articles on the current study but not on Hodge.

@@
